Title

### 2015-12-09 paper/paper.tex
adding to data section

Abstract Meaning Representation (AMR)\cite{amr_sembank} attempts to unify the
semantic representation of natural language sentences. Unlike syntactic
annotations, semantic annotations often differ for different semantic relations
(named entities, temporal entities, co-referencing, etc). AMR, by contrast,
provides a single, graphical representation of the logical meaning of a
sentence, which can be easily understood by both humans and computers. For
example, given the sentence ``A prosecutor in South Korea seized 80 kilograms
of drugs'', we can construct the following logical form and AMR.\\

@@

>>>>

Abstract Meaning Representation (AMR)\cite{amr_sembank} attempts to unify the
semantic representation of natural language sentences. Unlike syntactic
annotations, semantic annotations often differ for different semantic relations
(named entities, temporal entities, co-referencing, etc). AMR, by contrast,
provides a single, graphical representation of the logical meaning of a
sentence, which can be easily understood by both humans and computers.

@@

The dataset for this research was a corpus of AMR-annotated sentences obtained
from newswire data. Since the source text of the articles was unavailable, we
used a sliding window approach to generate ``paragraphs" of size $k$ from the
articles. For an article with $n$ sentences, we could generate paragraphs
containing sentences $(s_1,s_2,\ldots,s_k), (s_2,s_3,\ldots,s_k,s_{k+1}),
\ldots (s_{n-k},s_{n-k+1},\ldots,s_n)$.

An example sentence from our dataset, along with its first-order logic and AMR
representations, follows.
As an example from our dataset, ``A prosecutor in South Korea seized 80
kilograms of drugs'' would have the following first-order logical form and AMR
representation.\\
